Client-Side Indexes for Fast Full-Text Searching

### 2014-12-08 paper/paper.tex
added more to related work

There have been some 
Client-side database storage can improve the performance of data intensive websites by executing portions of web applications client-side and synchronizing with a web server.
\cite{benson2010sync}

@@

previous use cases for client side search engine:
client side application to capture search content to support web search
\cite{bharat2000searchpad}

personalization of search
\cite{teevan2005personalizing}

client side querying of search
\cite{bozzon2010liquid}

Search engines can be useful in the absence of connectivity on mobile phones. This system builds on a user study showing that revisitation is common.
\cite{balasubramanian2012findall}

>>>>

Though previous HTML standards and browser capabilities were more limited, the idea of using of the client side for data storage and data computation has been around for many years.

When it comes to search engines, specifically web search, prior work has found that 40\% to 60\% of search queries are re-finding queries~\cite{teevan2005personalizing}. This finding has lead to applications that store web content from the result of a search engine to improve speed and availability when the network is down~\cite{bozzon2010liquid,balasubramanian2012findall}. Prior work in this area has also highlighted how web search can often be a highly personal activity, and that web search should be personalized to the user to improve accuracy. Personal information can then be stored on the client side as this information is primarily useful for this particular client~\cite{teevan2005personalizing}.

With the increased use of mobile phones in recent years, many web applications are now accessed via a smartphone. Here too, studies have shown that many queries to search engines are for re-finding. Using a client-side database is potentially even more impactful for a mobile phone browser because network connectivity is much less robust. Researchers have demonstrated this feasiblity by building a standalone search application for Android~\cite{balasubramanian2012findall}. However, this search engine is not usable with other browsing apps or other phones. Because we build an extension on top of IndexedDB, our search engine will be able to work for all browsers, desktop or mobile, that support IndexedDB, which is the majority of them.

Client-side database storage can improve the performance of data intensive websites by executing portions of web applications client-side and synchronizing with a web server.
\cite{benson2010sync}

@@

Applications have also been built to take advantage of client-side storage
client side application to capture search content to support web search
\cite{bharat2000searchpad}
